\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2018-10-04 bare_conf.tex
some modifications of text.

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{~\\[-0.4ex]\large Michael Shell\\[0.3ex]\normalsize}
\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
Georgia Institute of Technology\\
Atlanta, Georgia 30332--0250\\
Email: {\tt ...}}
\and
\IEEEauthorblockN{~\\[-0.4ex]\large Homer Simpson\\[0.3ex]\normalsize}
\IEEEauthorblockA{Twentieth Century Fox\\
Springfield, USA\\
Email: {\tt homer@thesimpsons.com}}
\and
\IEEEauthorblockN{~\\[-0.4ex]\large Andrius Budrionis\\[0.3ex]\normalsize}
\IEEEauthorblockA{Vilnius Gediminas Technical University\\
Vilnius, Lithuania\\
Norwegian Centre for E-health Research\\
University Hospital of North Norway\\
Tromsø, Norway}}

@@

\begin{abstract}
%\boldmath
The abstract goes here.
The abstract goes here.
The abstract goes here.
The abstract goes here.
The abstract goes here.
The abstract goes here.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

\begin{IEEEkeywords}
Computer vision; Mobile application; Travel aid; Tactile. %
\end{IEEEkeywords}

@@

The key part of the proposed system is a smartphone device, connecting user interface and data processing components into a well-functioning ecosystem. Smartphone was selected due to its high availability and capability to perform required computations or forward visual information to the external server via the Internet connection. The cornerstone of the proposed solution is a wearable forehead belt, integrating two cameras and a tactile feedback device. Bone conductive headphones are suggested to facilitate audio feedback.

%\begin{wrapfigure}{r}{0.4\textwidth}
\begin{figure}
  \begin{center}
    \includegraphics[scale=0.7]{./img/cropped_diagram.pdf}  
  \end{center}
  \caption{Schematics of FRP device.}
  \label{fig:schematics}
\end{figure}

@@

Discussions on functionality and key features of the solution revealed a gap between the aims of the existing tools, which are often focused on advanced navigation and scene description features, and actual user needs. The end users highlighted that a simplistic solution for navigating is lacking. They were not excited about advanced object detection and scene description techniques, which may overcomplicate their daily life. Major focus was put on a easy to use and minimalistic tool, which can be trusted. Direction and approximate distance to obstacle were highlighted as major requirements. To our surprise, only 5-8 distinctive object classes (for instance, buss stop, pedestrian crossing, doors, stairs, etc) were of major importance while navigating. Additional information, such as type of a passing car, blossoming flowers in the park or person passing riding a bicycle was considered as overwhelming and distractive.

Social networking functionality was accepted as a potentially important feature allowing other users/volunteers to describe certain objects (for instance, temporary road works) with exact location and description. Navigating around such obstacles can be challenging for computer vision-based tools and may decrease user's trust in the tool. Integration of additional information from other users, governmental organizations and volunteers could be of high value for the visually impaired people.

%Povilai, paziurek ar cia viskas OK, pridek ka nors nuo saves
Computer vision technology is under rapid development and during last years made major breakthrough in performance and efficiency. Deep learning neural networks, which are de facto standard in modern image/video processing, are now well supported by software libraries and dedicated hardware built-in even in relatively low-power computational devices, such as smartphones. These devices are equipped with high-quality cameras, 4G Internet connectivity and sufficient computational power to perform initial data processing locally. The maturity of the aforementioned technologies suggest that our proposed computational aid for visually impaired persons may be highly feasible.

@@

Appearance, usability and cost of the final solution is of major importance to the users. The proposed assistive technology should replace/supplement the tool that visually impaired persons used for decades - the white cane. Using a white cane requires little to none training, has very low costs and is relatively reliable. It provides information on the surrounding objects 1-2 meters in front of the user. While the cane can used to detect a nearby obstacle, electronic travel aid could be beneficial for longer range (10-20m) route planning and object recognition. However, it should integrate seamlessly into the existing navigation practices of visually impaired people.

@@

%\textbf{Inference} subsystem consists of server computer with internet connection and set of computer vision algorithms, selected according to our methodology (see. Sec.~\ref{sec:method}): Faster RCNN object detector \cite{?}, trained to detect important objects (doors, floors, elevators, stairs, corridor junctions, etc.), CNN-RNN-based scene description \cite{Liu},\cite{Ren}, \cite{Dai}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, and possibly other modules.

@@

In this article we outlined an idea of complex computer vision-based sensor architecture, which can help to partially compensate impaired or lost human sight. Main improvements comparing to similar previous work (\cite{?}, \cite{?}) is: ability to use efficient (but still computationally intensive) modern computer vision algorithms via Internet connection, present the signal to the user by combined bone conductive headphone-tactile actuator, low cost and consequently increased potential availability of the device. Suggested architecture can be used as basis for various computer vision-based systems, allowing to help visually impaired users in everyday routines (e.g. outdoor/indoor navigation,...). On the other side, due to remotelly carried visual analysis, in some cases the suggested system may suffer from too large latency, its reliability depends on stability and quality of Internet connection. Such a problem partially may be solved in near future, when 5G networks will prevail.

@@

\bibitem{Caraiman} Caraiman, S., Morar, A., Owczarek, M.,Burlacu, A., Rzeszotarski, D., Botezatu, N., Herghelegiu, P., Moldoveanu, F., Strumillo, P., Moldoveanu, A. Computer Vision for the Visually Impaired: the Sound of Vision System. IEEE International Conference on Computer Vision Workshops, pp. 1480-1489, 2017.
\bibitem{Csapo} Csap\'{o}, A., Wers\'{e}nyi, G., Nagy, H., Stockman, T. A survey of assistive technologies and applications for blind users on mobile platforms: a review and foundation for research. Journal on Multimodal User Interfaces. Vol. 9, issule 4,  pp. 275-286, 2015.
\bibitem{Dai} Dai, J., Li, Y., He, K., Sun J. R-FCN: Object Detection via Region-based Fully Convolutional Networks. In Advances in neural information processing systems, pp. 379-387, 2016.
\bibitem{Poggi} Poggi, M., Mattoccia, S. A wearable mobility aid for the visually impaired based on embedded 3d vision and deep learning. Proceeding of IEEE Symposium on Compututers and Communication, pp. 208-213, 2016.
\bibitem{Zientara} Zientara, P.,A., Lee, S., Smith, G., H., Brenner, R., Itti, L., Rosson M., B., Carroll, J., M., Irick K., M., Narayanan, V. Third Eye: A shopping assistant for the visually impaired. Computer Vol. 50, Issue 2, pp. 16-24, 2017.
\bibitem{Liu} Liu, Ch., Mao, J., Sha, F., Yuille, A. Attention Correctness in Neural Image Captioning. Proceedings of the Thirty-First AAAI Conference on Artificial Intelligence, pp. 4176-4182, 2017.
\bibitem{Laina} Laina, I., Rupprecht, C., Belagiannis, V., Tombari, F., Navab, N. Deeper depth prediction with fully convolutional residual networks. Fourth International Conference on 3D Vision (3DV), pp. 239-248, 2016.
\bibitem{Ohn-Bar}  Ohn-Bar, E., Kitani, K., Asakawa, Ch. Personalized Dynamics Models for Adaptive Assistive Navigation Interfaces. arXiv:1804.04118, [cs.LG], 2018.
\bibitem{Ren} Ren, Sh., He, K., Girshick, R., and Sun, J.  Faster R-CNN: Towards real-time object detection with region proposal networks. In Advances in neural information processing systems, pp. 91-99, 2015.

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{~\\[-0.4ex]\large Povilas Daniu\v{s}is\\[0.3ex]\normalsize}
\IEEEauthorblockA{Vilnius Gediminas Technical University\\
Vilnius, Lithuania}
\and
\IEEEauthorblockN{~\\[-0.4ex]\large Audrius Indriulionis\\[0.3ex]\normalsize}
\IEEEauthorblockA{Vilnius Gediminas Technical University\\
Vilnius, Lithuania}
\and
\IEEEauthorblockN{~\\[-0.4ex]\large Andrius Budrionis\\[0.3ex]\normalsize}
\IEEEauthorblockA{Vilnius Gediminas Technical University\\
Vilnius, Lithuania\\
Norwegian Centre for E-health Research\\
University Hospital of North Norway\\
Tromsø, Norway}}

@@

\begin{abstract}
%\boldmath
In this short article we describe and discuss architecture of computer vision-based system for partial compensation of lost or impaired human vision.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

\begin{IEEEkeywords}
Computer vision; Mobile application; Aid for blind and visually impaired; Tactile feedback; Impaired human vision compensation.%
\end{IEEEkeywords}

@@

The key part of the proposed system is a smartphone device, connecting user interface and data processing components into a well-functioning ecosystem. Smartphone was selected due to its high availability and capability to perform required computations or forward visual information for processing to the external server via the Internet connection.

The cornerstones of the proposed solution are its inferface and external server, capable running computationally demanding vision processing algorithms.

The interface consists of a wearable forehead belt, integrating RGB and depth cameras, tactile feedback device and bone conductive headphones. Altough more expensive than standard ones, bone conductive headphones allow the user to perceive audio information from the surrounding environment, which is essential for the visually impaired people.

External server processes received visual data according to user request with computer vision algorithms: faster RCNN object detector \cite{Ren}, trained to detect important objects, CNN-RNN-based scene description \cite{Liu}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, and other algorithms, and transmits feedback signal back to the smartphone device for presenting to the user via the above described interface.

%\begin{wrapfigure}{r}{0.4\textwidth}
\begin{figure}
  \begin{center}
    \includegraphics[scale=0.7]{./img/cropped_diagram.pdf}  
  \end{center}
  \caption{Schematics of vision compensation device.}
  \label{fig:schematics}
\end{figure}

@@

Discussions on functionality and key features of the solution revealed a gap between the aims of the existing tools, which are often focused on advanced navigation and scene description features, and actual user needs. The end users highlighted that a simplistic solution for navigating is lacking. 
%They were not excited about advanced object detection and scene description techniques, which may overcomplicate their daily life. 
Major focus was put on a easy to use and minimalistic tool, which can be trusted. Object detection, and direction and approximate distance to obstacle were highlighted as major requirements. To our surprise, only 5-8 distinctive object classes (for instance, buss stop, pedestrian crossing, doors, stairs, etc) were of major importance while navigating. Additional information, such as type of a passing car, blossoming flowers in the park or person passing riding a bicycle was considered as overwhelming and distractive. Another important functionality required by end users was navigation aid.

%Social networking functionality was accepted as a potentially important feature allowing other users/volunteers to describe certain objects (for instance, temporary road works) with exact location and description. Navigating around such obstacles can be challenging for computer vision-based tools and may decrease user's trust in the tool. Integration of additional information from other users, governmental organizations and volunteers could be of high value for the visually impaired people.

%Povilai, paziurek ar cia viskas OK, pridek ka nors nuo saves
Computer vision technology is under rapid development and during last years made major breakthrough in performance and efficiency. Deep learning neural networks, which are de facto standard in modern image/video processing, are now well supported by software libraries and dedicated hardware built-in even in relatively low-power computational devices, such as smartphones. These devices are also equipped with 4G Internet connectivity and sufficient computational power to perform initial data processing locally. The maturity of the aforementioned technologies suggest that our proposed computational aid for visually impaired persons may be highly feasible.

@@

Appearance, usability and cost of the final solution is of major importance to the users. The proposed assistive technology should supplement the tool that visually impaired persons used for decades - the white cane. Using a white cane requires little to none training, has very low costs and is relatively reliable. It provides information on the surrounding objects 1-2 meters in front of the user. While the cane can used to detect a nearby obstacle, electronic travel aid could be beneficial for longer range (10-20m) route planning and object recognition. However, it should integrate seamlessly into the existing navigation practices of visually impaired people.

@@

%\textbf{Inference} subsystem consists of server computer with internet connection and set of computer vision algorithms, selected according to our methodology ed (see. Sec.~\ref{sec:method}): Faster RCNN object detector \cite{?}, trainto detect important objects (doors, floors, elevators, stairs, corridor junctions, etc.), CNN-RNN-based scene description \cite{Liu},\cite{Ren}, \cite{Dai}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, and possibly other modules.

@@

In this article we outlined an idea of complex computer vision-based sensor architecture, which can help to partially compensate impaired or lost human sight. Main improvements comparing to similar previous work (\cite{?}, \cite{?}) are: ability to use efficient (but still computationally intensive) modern computer vision algorithms via Internet connection, present the signal to the user by combined bone conductive headphone-tactile actuator, low cost and consequently increased potential availability of the device. The suggested system integrates well with the main blind person's aid - the white cane. The hardware architecture can be used as the basis for various computer vision-based software modules, allowing to help visually impaired users in everyday routines (e.g. outdoor/indoor navigation, object/face recognition, obstacle detection, navigation). On the other side, due to remotelly carried visual analysis, in some cases the suggested system may suffer from too large latency, its reliability depends on stability and quality of Internet connection.

%Such a problem partially may be solved in near future, when 5G networks will prevail.

@@

\bibitem{Caraiman} Caraiman, S., Morar, A., Owczarek, M.,Burlacu, A., Rzeszotarski, D., Botezatu, N., Herghelegiu, P., Moldoveanu, F., Strumillo, P., Moldoveanu, A. Computer Vision for the Visually Impaired: the Sound of Vision System. IEEE International Conference on Computer Vision Workshops, pp. 1480-1489, 2017.
\bibitem{Csapo} Csap\'{o}, A., Wers\'{e}nyi, G., Nagy, H., Stockman, T. A survey of assistive technologies and applications for blind users on mobile platforms: a review and foundation for research. Journal on Multimodal User Interfaces. Vol. 9, issule 4,  pp. 275-286, 2015.
%\bibitem{Dai} Dai, J., Li, Y., He, K., Sun J. R-FCN: Object Detection via Region-based Fully Convolutional Networks. In Advances in neural information processing systems, pp. 379-387, 2016.
\bibitem{Poggi} Poggi, M., Mattoccia, S. A wearable mobility aid for the visually impaired based on embedded 3d vision and deep learning. Proceeding of IEEE Symposium on Compututers and Communication, pp. 208-213, 2016.
\bibitem{Zientara} Zientara, P.,A., Lee, S., Smith, G., H., Brenner, R., Itti, L., Rosson M., B., Carroll, J., M., Irick K., M., Narayanan, V. Third Eye: A shopping assistant for the visually impaired. Computer Vol. 50, Issue 2, pp. 16-24, 2017.
\bibitem{Liu} Liu, Ch., Mao, J., Sha, F., Yuille, A. Attention Correctness in Neural Image Captioning. Proceedings of the Thirty-First AAAI Conference on Artificial Intelligence, pp. 4176-4182, 2017.
\bibitem{Laina} Laina, I., Rupprecht, C., Belagiannis, V., Tombari, F., Navab, N. Deeper depth prediction with fully convolutional residual networks. Fourth International Conference on 3D Vision (3DV), pp. 239-248, 2016.
\bibitem{Ohn-Bar}  Ohn-Bar, E., Kitani, K., Asakawa, Ch. Personalized Dynamics Models for Adaptive Assistive Navigation Interfaces. arXiv:1804.04118, [cs.LG], 2018.
\bibitem{Ren} Ren, Sh., He, K., Girshick, R., and Sun, J.  Faster R-CNN: Towards real-time object detection with region proposal networks. In Advances in neural information processing systems, pp. 91-99, 2015.
